MSstatsPTM: Statistical relative quantification of post-translational modifications in bottom-up mass spectrometry-based proteomics

### 2022-06-12 main/MSstatsPTM_Main.tex
small

\begin{equation}
\begin{aligned}
H_{0}: \Delta = \mu_{1}^{\ast} - \mu_{2}^{\ast} = 0 \\
H_{a}: \Delta = \mu_{1}^{\ast} - \mu_{2}^{\ast} \neq 0
\end{aligned}
\label{eq:conv_null_hyp}
\end{equation}
However, these population parameters are inherently convoluted with changes in the unmodified protein. To account for this, we must estimate the relative abundance of the unmodified protein in conditions $1$ and $2$, denoted by $\mu_1$ and $\mu_2$. We estimate the quantities $\hat{\mu}_i$ and $\widehat{SE(\hat{\mu}_i)}$ in the same way as for the PTM site, using their corresponding features and observations and resulting in an estimated mean abundance. These estimates are used to adjust the quantities estimated for the PTM, resulting in the new Null and Alternative Hypotheses seen in Equation \ref{eq:null_hyp}.

>>>>

\begin{equation}
\begin{aligned}
H_{0}: \Delta = \mu_{1}^{\ast} - \mu_{2}^{\ast} = 0 \\
H_{a}: \Delta = \mu_{1}^{\ast} - \mu_{2}^{\ast} \neq 0
\end{aligned}
\label{eq:conv_null_hyp}
\end{equation}
However, these population parameters are inherently convoluted with changes in the unmodified protein. To account for this, we must estimate the relative abundance of the unmodified protein in conditions $1$ and $2$, denoted by $\mu_1$ and $\mu_2$. We estimate \todo{OV: our method, or everyone?} the quantities $\hat{\mu}_i$ and $\widehat{SE(\hat{\mu}_i)}$ in the same way as for the PTM site, using their corresponding features and observations and resulting in an estimated mean abundance. These estimates are used to adjust the quantities estimated for the PTM, resulting in the new Null and Alternative Hypotheses seen in Equation \ref{eq:null_hyp}.
